---
title: "Take 2 - March 2nd"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(reactable)
library(tidyverse)
library(colorblindr)
library(plotly)
#theme_set(theme_minimal(legend.position= c(0.8, 0.2)))

```


Data Description {.sidebar}
===========
This is a built-in dataset with [R](cran.r-project.org). It's a *fun* data set about **flowers**.

The title does not show up unless it's in mobile mode, or unless the window is squished really small. The title of this sidebar is **Data Description**


# iris
More text to inlcude before the plots and things.

Column {data-width=650}
-----------------------------------------------------------------------


### Scatterplot

Little baby description about a little baby plot.

```{r}


ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(color = Species)) +
  geom_smooth(color = "magenta") +
  scale_fill_OkabeIto() +
  theme_minimal()
  

```

Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Sepal Length by Species

```{r iris-bar, fig.height=6}

iris %>% 
  group_by(Species) %>% 
  summarize(mean_sepal_length = mean(Sepal.Length)) %>% 
  ungroup() %>% 
  mutate(Species = fct_reorder(Species, mean_sepal_length)) %>% 
  ggplot(aes(Species, mean_sepal_length)) +
  geom_col(fill = "cornflowerblue") +
  coord_flip() +
  scale_y_continuous(expand = c(0,0)) +
  labs(
    x = NULL,
    y = "Mean Sepal Length"
  ) +
  theme_classic(base_size = 15) 

```

### Iris Table

```{r}

reactable::reactable(iris)

```

# mtcars

Column {data-width=350}
-----------------------------------------------------------------------

### Chart A

```{r plot11}

ggplot(mpg, aes(displ, cty)) +
  geom_point(color = "orange") +
  geom_smooth() +
  facet_wrap(~class, ncol = 3) +
  labs(title = "Classic Plot w. Class But Different")



```


Column {data-width=650}
-----------------------------------------------------------------------

### Chart B

```{r}

p <- ggplot(mpg, aes(displ, cty)) +
  geom_point(color = "cornflowerblue") +
  geom_smooth() +
  facet_wrap(~class) +
  labs(title = "Classic Plot w. Class")

ggplotly(p)


```

### Chart C

```{r plot31, fig.height = 2}

ggplot(mpg, aes(displ, cty)) +
  geom_point(color = "magenta") +
  geom_smooth() +
  labs(title = "Classic Plot")

```

# reactable